---
title: "Trial Code"
author: "Aoi Kawahara"
date: "2025-02-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About trial.Rmd

本番は30万件以上のポストを扱う予定だが、使用する変数等の挙動確認のため、trialではまず1,000件のポストで分析を実行してみる。

I will deal with more than 300k posts for the actual thesis. This trial is conducted on 1k posts for the purpose of testing the code and functions below.

## Load libraries

```{r library}
library(data.table)
library(tidyverse)
library(tidytext)
library(wordcloud)
library(topicmodels)
library(tm)
library(dplyr)
library(qdap)
library(plotrix)
library(dendextend)
library(tokenizers)
library(textclean)
library(ggthemes)
```

## Load data

```{r df}
setwd('/Users/aoikawahara/Library/CloudStorage/OneDrive-KULeuven/Leuven/01_Master Thesis/Workplace')

df = fread("data/part_1/may_july_chunk_1.csv.gz")
```

## Select necessary columns

-   Select English posts / テキストが英語

-   Transform a data frame with columns (text, epoch) / カラム名がtextとepochだけののデータフレームに変換

```{r subset_df}

df <- df[1:1000,] %>%
  subset(lang == 'en') %>%
  subset(select = c(text, epoch, retweetCount, likeCount)) %>%
  mutate(id = row_number())
```

## Fast descriptives

```{r descriptives}
df_epoch <- data.frame(table(df$epoch))
colnames(df_epoch) <- c("epoch", "count")

ggplot(df_epoch, aes(x = as.numeric(epoch), y = count)) +
  geom_line() +
  labs(title = "Number of posts")
```

## Clean text

From Kanmaz(2023)

-   Lowercasing the characters

-   Removal of stopwords

-   Stemming the words

-   Removal of hashtags

-   Removal of user mentions

-   Removal of links

-   Removal of emojis

```{r text_organization}
qdap_clean <- function(x) {
  x <- replace_abbreviation(x)            　 # "Dr." → "Doctor"
  x <- replace_contraction(x)                # "can't" → "cannot"
  x <- replace_ordinal(x)                    # "1st" → "first"
  x <- gsub("\\d+", "", x)                   # Removal of numbers
  x <- tolower(x)                            # Lowercasing the characters
  x <- str_remove_all(x, "#\\S+") 　　　　　 # Removal of hashtags
  x <- str_remove_all(x, "@\\S+")  　　　　　# Removal of user mentions
  x <- replace_symbol(x)                     # "&" → "and"
  x <- str_remove_all(x, "http[s]?://\\S+")  # Removal of links
  x <- replace_emoji(x)                      # Emojis → Word forms equivalents
  return(x)
  }

tm_clean <- function(corpus) {
  corpus <- tm_map(corpus, removePunctuation)  # Remove punctuation (句読点)
  corpus <- tm_map(corpus, stripWhitespace)    # 余分な余白
  corpus <- tm_map(corpus, removeWords, stopwords("en"))    # Remove stopwords
  corpus <- tm_map(corpus, content_transformer(stemDocument))  # Stemming
  return(corpus)}

qdap_cleaned_df <- qdap_clean(df$text)
corp <- VCorpus(VectorSource(qdap_cleaned_df)) %>%
  tm_clean()

cleaned_text <- lapply(corp, function(doc) doc$content)
df_cleaned_text <- data.frame(id = seq_along(cleaned_text),
                              text = unlist(cleaned_text),
                              stringsAsFactors = FALSE)

# qdap_cleanの挙動確認
df$text[25]
qdap_cleaned_df[25]
cleaned_text[25]
```

## Create Term Document Matrix

```{r tdm}
tdm <- TermDocumentMatrix(corp)
tdm_m <- as.matrix(tdm)

tdm_m[which(is.na(tdm_m))] <- 0
```

## Plot bar chart - term frequency

```{r bar_plot}
freq <- rowSums(tdm_m)
freq <- sort(freq, decreasing = TRUE)

barplot(freq[1:20], col = "tan", las = 2)
```

## Plot WordCloud

```{r wordcloud}

wordcloud(names(freq), freq, max.words = 100, color = "blue")
```

## Word Association "biden"

```{r assoc_biden}
assoc <- findAssocs(tdm, "biden", 0.12)
assoc

assoc_df <- list_vect2df(assoc, col2 = "word", col3 = "score")

ggplot(assoc_df, aes(score, word)) + 
  geom_point(size = 3) +
  labs(title = "Words associated with 'biden'") +
  theme_minimal()
```

## Word Association "trump"

```{r assoc_trump}
assoc_trump <- findAssocs(tdm, "trump", 0.15)

assoc_trump_df <- list_vect2df(assoc_trump, col2 = "word", col3 = "score")

ggplot(assoc_trump_df, aes(score, word)) + 
  geom_point(size = 3) +
  labs(title = "Words associated with 'trump'") +
  theme_minimal()
```

## LDA with 3 topics

Kanmaz(2023)は3\~25 topicsで試し、coherence scoreを比較していた。

```{r lda_3}
dtm <- DocumentTermMatrix(corp)

row_sums <- rowSums(as.matrix(dtm))  # 空白の行がある確認
dtm <- dtm[row_sums > 0, ]  # 単語が含まれていない空の文書を削除

lda_3 <- LDA(dtm, k = 3, method = "Gibbs", control = list(seed = 42))

glimpse(lda_3)

lda_3 <- lda_3 %>% 
  tidy(matrix = "beta")
lda_3 %>% 
  arrange(desc(beta))

# Visualization of top 15 terms by topic (3topics)
word_3 <- lda_3 %>% 
  group_by(topic) %>% 
  slice_max(beta, n = 15) %>% 
  ungroup() %>%
  mutate(term2 = fct_reorder(term, beta))

ggplot(word_3, aes(x = term2, y = beta, fill = as.factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

## Select number of topics for LDA model

(Coherence score...モデルによって生成されたトピックの一貫性と解釈可能性を評価。)

<https://cran.r-project.org/web/packages/ldatuning/vignettes/topics.html>

```{r select_k}
library("ldatuning")

result <- FindTopicsNumber(
  dtm,
  topics = seq(from = 2, to = 15, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  mc.cores = 2L,
  verbose = TRUE)

FindTopicsNumber_plot(result)
```

It can be estimated that the 5 topcs is the most optimal?

## LDA with 5 topics

```{r lda_5}
lda_5 <- LDA(dtm, k = 5)
glimpse(lda_5)

lda_5 <- lda_5 %>% 
  tidy(matrix = "beta")
lda_5 %>% 
  arrange(desc(beta))

# Visualization of top 10 terms by topic (9topics)
word_5 <- lda_5 %>% 
  group_by(topic) %>% 
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  mutate(term2 = fct_reorder(term, beta))

ggplot(word_5, aes(x = term2, y = beta, fill = as.factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

## TF-IDF Vectorization

```{r tfidf}
tfidf_tdm <- TermDocumentMatrix(corp, control = list(weighting = weightTfIdf))
tfidf_tdm_m <- as.matrix(tfidf_tdm)

tfidf_tdm_m[c("biden", "trump", "maga"), 20:30]

tfidf_freq <- rowSums(tfidf_tdm_m)
tfidf_freq <- sort(tfidf_freq, decreasing = TRUE)

wordcloud(names(tfidf_freq), tfidf_freq, max.words = 40, color = "blue")
```

## Sentiment Analysis - Polarity (fast & dirty)

```{r polarity}
pol <- polarity(df_cleaned_text$text[1:891])
summary(pol$all$polarity)

ggplot(pol$all, aes(x = polarity, y = ..density..)) + 
  geom_histogram(binwidth = 0.25, fill = "#bada55", colour = "grey60") +
  geom_density(size = 0.75) +
  theme_gdocs()
```

## Sentiment Analysis - Polarity (tidy)

```{r polarity_tidy}
tidy_texts <- df_cleaned_text %>% 
  unnest_tokens(word, text)

tidy_texts <- tidy_texts %>% 
  group_by(id) %>% 
  mutate(original_word_order = seq_along(word))

bing <- get_sentiments("bing")

pos_neg <- tidy_texts %>% 
  inner_join(bing, by = c("word" = "word")) %>%
  count(sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(polarity = positive - negative)

ggplot(pos_neg, aes(x = polarity, y = ..density..)) + 
  geom_histogram(binwidth = 1, fill = "#bada55", colour = "grey60") +
  geom_density(size = 0.75) +
  theme_gdocs()
```

## Organize positive/negative words

```{r pos}
pos_terms <- df_cleaned_text %>%
  mutate(polarity = pol$all$polarity) %>%
  filter(polarity > 0) %>%
  pull(text) %>%
  paste(collapse = " ")

neg_terms <- df_cleaned_text %>%
  mutate(polarity = pol$all$polarity) %>%
  filter(polarity < 0) %>%
  pull(text) %>% 
  paste(collapse = " ")

all_corp <- c(pos_terms, neg_terms) %>% 
  VectorSource() %>% 
  VCorpus()

all_tdm <- TermDocumentMatrix(all_corp,
                              control = list(weighting = weightTfIdf))

all_tdm_m <- as.matrix(all_tdm)
colnames(all_tdm_m) <- c("positive", "negative")
all_tdm_df <- as.data.frame(all_tdm_m)
all_tdm_df$term <- rownames(all_tdm_df)

comparison.cloud(all_tdm_m, max.words = 18, colors = c("darkgreen","darkred"))
```

## Bar plot of positive terms

```{r bar_pos}
order_by_pos <- all_tdm_df %>%
  arrange(desc(positive)) %>%
  head(20)

ggplot(order_by_pos, aes(x = reorder(term, positive), y = positive)) +
  geom_bar(stat = "identity", fill = "darkgreen") +
  labs(title = "Top 20 Terms by Positive Score",
       x = "Terms",
       y = "Positive") +
  coord_flip() +
  theme_gdocs() 
```

## Bar plot of negative terms

```{r bar_neg}
order_by_neg <- all_tdm_df %>%
  arrange(desc(negative)) %>%
  head(20)

ggplot(order_by_neg, aes(x = reorder(term, negative), y = negative)) +
  geom_bar(stat = "identity", fill = "darkred") +
  labs(title = "Top 20 Terms by Negative Score",
       x = "Terms",
       y = "Negative") +
  coord_flip() +
  theme_gdocs() 
```

## Polarity vs Word effort

```{r pol_n}
pos_neg_pol <- tidy_texts %>% 
  count(id) %>%
  inner_join(pos_neg) %>%
  mutate(pol = ifelse(polarity >= 0, "Positive", "Negative"))

ggplot(pos_neg_pol, aes(polarity, n, color = pol)) + 
  geom_point(alpha = 0.25) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_gdocs() +
  ggtitle("Relationship between word effort & polarity")
```

## Sentiment vs Like count

```{r sent_like}

df_sent <- df %>% 
  inner_join(pos_neg, by = c("id" = "id")) %>%
  select(c(id, retweetCount, likeCount, polarity))

ggplot(df_sent, aes(x = polarity, y = likeCount)) + 
  geom_point() +
  theme_minimal() +
  ggtitle("Relationship between like count & polarity")

df_sent_outlier <- df_sent %>%
  filter(likeCount < 2000)

ggplot(df_sent_outlier, aes(x = polarity, y = likeCount)) + 
  geom_point() +
  theme_minimal() +
  ggtitle("Relationship between like count & polarity")
```

## Sentiment vs Retweet count

```{r sent_ret}
ggplot(df_sent, aes(x = polarity, y = retweetCount)) + 
  geom_point() +
  theme_minimal() +
  ggtitle("Relationship between retweet count & polarity")

df_sent_outlier <- df_sent %>%
  filter(likeCount < 300)

ggplot(df_sent_outlier, aes(x = polarity, y = likeCount)) + 
  geom_point() +
  theme_minimal() +
  ggtitle("Relationship between like count & polarity")
```
